Research

### 2025-08-17 index.qmd
mainfont: Lato monofont: Roboto
css font
styles2.css
job website

---
title: "Shaokang Yang"
mainfont: Lato
monofont: Roboto
---

-   **Ph.D. in Business Information Technology (Expected)**

Virginia Polytechnic Institute and State University

-   **M.Sc. in Data Science and Economics**

University of Milan

-   **Bachelor of Engineering/Bachelor of Economics**

Jimei University

>>>>

---
title: "Shaokang Yang"
format:
  html:
    css: styles2.css
class: custom-font-pos
---

Department of Business Information Technology

Pamplin College of Business, Virginia Tech

Blacksburg, VA 24061

Website: [shaokang-yang.net](shaokang-yang.net)

-   **Virginia Polytechnic Institute and State University**

    Ph.D. in Business Information Technology (2026, Expected)

    M.A. in Data Analysis and Applied Statistics

-   **University of Milan**

    M.Sc. in Data Science and Economics

-   **Jimei University**

    Bachelor of Engineering; Bachelor of Economics

### 2025-08-17 research.qmd
Research blog moving
job website

>>>>

## Research Interests

-   Topics: Healthcare policy analysis, healthcare IT
-   Methodologies: Causal inference with econometrics, machine learning, statistical learning

## Working Papers

-   **Smartphone Use, Social Support, and Sleep Health** Shaokang Yang, Idris Adjerid. \[[SSRN](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5368531)\] –*Under Review at Information Systems Research*

-   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time** Shaokang Yang, Idris Adjerid. – *In preparation for submission*\

<!-- -->

-   ***The Abortion War: When Restrictions Meet Technology** Shaokang Yang, Idris Adjerid.* – *In preparation for submission*

## Presentations

-   **Friends over Feeds: How Social Smartphone Use Reduces Screen Time.**\
    Shaokang Yang, Idris Adjerid
    -   Conference on Health IT and Analytics (CHITA) — Apr 2025, Austin, TX
    -   INFORMS Annual Meeting — Oct 2024, Seattle, WA
-   **Smartphone Use, Social Support, and Sleep Health.**\
    Shaokang Yang, Idris Adjerid
    -   Conference on Health IT and Analytics (CHITA) — May 2024, Washington, DC
    -   33rd Annual POMS Conference — May 2023, Orlando, FL
    -   Conference on Health IT and Analytics (CHITA) — May 2023, Washington, DC
